### 2021-06-18 paper/model/policies.tex
Rewrite policies section in model appendix.

\subsection{Reducing Numbers of Contacts Through Policies}
\label{sec:policies}

The main motivation of our model is to predict the effect of policies that affect the
number of contacts people have. Examples range from school closures and lockdowns to
more nuanced policies such as mandatory quarantines for symptomatic individuals or a
class splitting policy where only half of the students come to school in person and the
other half joins digitally with weekly rotation.

Instead of thinking of policies as completely replacing how many contacts people have,
it is often more helpful to think of them as adjusting the pre-pandemic number of
contacts.

Therefore, we implement policies as a step that happens after the number of contacts is
calculated but before individuals are matched.

On an abstract level, a policy is a functions that modifies the number of contacts of
one contact type. For example, school closures simply set all school contacts to zero. A
lockdown where only essential workers are allowed to work means that approximately two
thirds of the working population have zero work contacts and the rest has the same
number of contacts as before.

This, in conjunction with our fine-grained contact types, allows us to easily implement
a wide variety of policies. Allowing policies to depend on the health states of the
entire population means that adaptive lockdowns where, for example, schools close when a
certain threshold of infections is surpassed at the county level would be as simple as
determining which counties are above the threshold and then setting all school contacts
in these counties to zero.

The dependency of policies on health states also makes it possible to model contact
tracing. For example, a policy could check whether each child has a classmate who's
received a positive test result and then bar all children of that class from attending
school.

Some policies can be easily implemented if the background characteristics are suitably
extended. For example, a schooling policy with A/B schooling, where each half attends
school every other week can be implemented by storing whether the child would attend in
even or odd weeks in the background characteristics and then using that information in
the policy function.

For some policies the exact effect on each contact type is not easy to determine. If
this refers to a policy during the estimation period, it is possible to estimate such
parameters by fitting the model to time series data of infection rates. This is only
possible if the policy was not active during the whole estimation period and thus the
infection probabilities can be identified separately. If instead it refers to a policy
that we want to simulate, we make a scenario analysis in which the model is simulated
with several assumptions about how the policy affects the number of contacts.

>>>>

\subsection{Reducing Numbers of Contacts via NPIs}
\label{sec:policies}

Our model makes it very easy to model a wide range of NPIs, either in isolation or
simultaneously. This is important for two reasons: Firstly, it allows to predict and
quantify the effect of novel NPIs. Secondly, it allows to model the actually implemented
policy environment in great detail, which is necessary to use use the full time series
of infections and fatality rates to estimate the model parameters.\footnote{
See \citet{Avery2020} for an explanation why it can be harmful to use too long time
series to estimate simple SEIR type models.}

Instead of thinking of policies as completely replacing how many contacts people have,
it is often more helpful to think of them as adjusting the pre-pandemic number of
contacts. Therefore, we implement policies as a step that happens after the number of contacts is
calculated but before individuals are matched.

On an abstract level, a policy is a functions that modifies the number of contacts of
one contact type. This function can be random or deterministic. For example, school
closures simply set all school contacts to zero. A work from home mandate leads to a
share of workers staying home every day whereas those who cannot work from home are
unaffected. Hygiene measures at work randomly reduce the number of infectious contacts
for all workers who still go to work.

Policies can also interact. For example, school vacations are temporally reducing school
contacts to zero while at the same time increasing other contacts to account for
increased leisure activities and family visits during this time. This is important to
reproduce the finding that school vacations do not reduce infection numbers even though
schools lead to infections when open \citep{Isphording2021}.

The most complex policies are typically found in the education sector. Since the
beginning of 2021 schools have switched back and fourth between full closures,
split class approaches with alternating schedules for some or all age groups and
reopening while maintaining hygiene measures. On top of that there are different
policies for allowing young students whose parents work full time to attend school
even on days where they normally would not. For details on how we calibrate these
policies see Section~\ref{subsec:policies_seasonality}.

Importantly, policies can depend on the health states of participating individuals.
This allows to quarantine entire school classes if one student tested positive or
to implement official or private contact tracing.

For some policies the exact effect on each contact type is not easy to determine. If
this refers to a policy has been active during the estimation period, it is possible to
estimate such parameters by fitting the model to time series data of infection rates.
This is only possible if the policy was not active during the whole estimation period
and thus the infection probabilities can be identified separately. We do this to account
for hygiene measures at school and in the workplace that have been in effect since
November 2020.
